---
title: "nixpkgs:r-updates failures and package rankings"
format: 
  html_document:
    includes:
      in_header: header.html
---

```{r, include = FALSE}

eval_web_url <- paste(
    base_url,
    "eval",
    targets::tar_read(latest_evaluation), sep = "/"
) 

targets::tar_load(packages_df_with_rank)

# if everything fails, stop here
stopifnot("Table has error’d" = !is.null(packages_df_with_rank))

```

The tables below are a result of the hydra evaluation `r eval_web_url`, 
(latest build: `r strftime(targets::tar_read(latest_eval_date), usetz = TRUE)`).
Here, they include the
percentile of the package as computed by the `{packageRank}` package, as well as
a link to the PR to fix the build if it has been opened or if it's been merged
already. In the case of Bioconductor packages, percentile is calculated based on
the download count from here
[this csv](https://bioconductor.org/packages/stats/bioc/bioc_pkg_scores.tab).

The action generating the website runs each day at midnight. Do check the
original on Hydra from time to time though, because I can't guarantee that all
packages do show here. They should, but who knows. If the pull request fixing
the package doesn't follow the naming convention "rPackages.packagename: blab
bal" it likely won't show up here.

This is the table for CRAN packages. The greater the percentile, the more
popular the package:

```{r echo=FALSE, message=FALSE}
targets::tar_load(final_results)

reactable::reactable(final_results,
  columns = list(log_link = reactable::colDef(html = TRUE),
                 PR = reactable::colDef(html = TRUE),
                 percentile = reactable::colDef(defaultSortOrder = "desc")),
  defaultSorted = "percentile",
  filterable = TRUE
)

```

This is the table for Bioconductor packages. The greater the percentile, the 
more popular the package.

```{r, echo=FALSE, message=FALSE}
targets::tar_load(final_results_bioc)

reactable::reactable(final_results_bioc,
  columns = list(log_link = reactable::colDef(html = TRUE),
                 PR = reactable::colDef(html = TRUE),
                 percentile = reactable::colDef(defaultSortOrder = "desc")),
  defaultSorted = "percentile",
  filterable = TRUE
)

```

This table lists PRs to get an easy overview:


```{r, echo = FALSE}
targets::tar_load(prs_df)

reactable::reactable(prs_df,
  columns = list(PR = reactable::colDef(html = TRUE)),
  filterable = TRUE
)

```


Source code: https://github.com/b-rodrigues/nixpkgs-r-updates-fails

Rendered last: `r Sys.time()`
