---
title: "nixpkgs:r-updates failures and package rankings"
format: html
---


```{r, include = FALSE}

targets::tar_load(last_jobset_url)

targets::tar_load(results_table_with_rank)
targets::tar_load(open_prs)

# if everything fails, stop here
stopifnot("Table has error’d" = !is.null(results_table_with_rank))

results_df <- subset(results_table_with_rank$package.data,
                     select = c(-date, -total.downloads, -total.packages, -downloads))


```

The table below can be found at `r last_jobset_url`, but here it includes the rank of the package
as computed by the `{packageRank}` package, as well as a link to the PR to fix the build
if it has been opened. For now, a package that doesn't build because one of its dependencies
is broken is not linked to its dependency's open PR.

The action generating the website runs each day at midnight. Do check the original on Hydra,
because Bioconductor packages are not listed, nor packages for which somehow {packageRank}
can't find a ranking.

```{r, echo = FALSE}
targets::tar_load(failing_jobs)

merge(failing_jobs, results_df) |>
  merge(open_prs, all.x = TRUE) |>  
  subset(select = -`X.`) |> 
  reactable::reactable(columns = list(build = reactable::colDef(html = TRUE),
                                      PR = reactable::colDef(html = TRUE)),
                       defaultSorted = "rank",
                       filterable = TRUE
   )

```

Source code: https://github.com/b-rodrigues/nixpkgs-r-updates-fails

Rendered last: `r Sys.time()`
