---
title: "nixpkgs:r-updates failures and package rankings"
format: 
  html_document:
    includes:
      in_header: header.html
---

```{r, include = FALSE}

targets::tar_load(last_jobset_still_fail_url)

targets::tar_load(packages_df_with_rank)

# if everything fails, stop here
stopifnot("Table has error’d" = !is.null(packages_df_with_rank))

```

The table below can be found at `r last_jobset_still_fail_url`, but here it
includes the rank of the package as computed by the `{packageRank}` package, as
well as a link to the PR to fix the build if it has been opened or if it's been
merged already. In the case of Bioconductor packages, package rank is directly
obtained from [this
csv](https://bioconductor.org/packages/stats/bioc/bioc_pkg_scores.tab) and the
rank is actually the monthly average of unique IP adresses that download the
package, so the higher, the better. If a package doesn't build because one of
its dependencies is broken, and if a PR fixing the broken dependency has been
opened, then each package that depends upon this dependency gets linked to said
PR.

The action generating the website runs each day at midnight. Do check the
original on Hydra from time to time though, because I can't guarantee that all
packages do show here. They should, but who knows. If the pull request fixing
the package doesn't follow the naming convention "rPackages.packagename: blab
bal" it likely won't show up here.

This is the table for CRAN packages. The lower the rank, the more popular the
package:

```{r, echo = FALSE}
targets::tar_load(final_results)

reactable::reactable(final_results,
  columns = list(build = reactable::colDef(html = TRUE),
                 PR = reactable::colDef(html = TRUE)),
  defaultSorted = "rank",
  filterable = TRUE
)

```

This is the table for Bioconductor packages. The rank is what they call the
*download score* which is *the average number of distinct IPs that "hit" the
package each month for the last 12 months (not counting the current month)*, so
the higher the rank, the more popular that package is:

```{r, echo = FALSE}
targets::tar_load(final_results_bioc)

reactable::reactable(final_results_bioc,
  columns = list(build = reactable::colDef(html = TRUE),
                 PR = reactable::colDef(html = TRUE),
                 rank = reactable::colDef(defaultSortOrder = "desc")),
  defaultSorted = "rank",
  filterable = TRUE
)

```

Source code: https://github.com/b-rodrigues/nixpkgs-r-updates-fails

Rendered last: `r Sys.time()`
