---
title: "nixpkgs:r-updates failures and package rankings"
format: 
  html_document:
    includes:
      in_header: header.html
---

```{r, include = FALSE}

targets::tar_load(last_jobset_still_fail_url)

targets::tar_load(packages_df_with_rank)

# if everything fails, stop here
stopifnot("Table has error’d" = !is.null(packages_df_with_rank))

```

The table below can be found at `r last_jobset_still_fail_url`, but here it includes the
rank of the package as computed by the `{packageRank}` package, as well as a
link to the PR to fix the build if it has been opened or if it's been merged
already. If a package doesn't build because one of its dependencies
is broken, and if a PR fixing the broken dependency has been opened, then each
package that depends upon this dependency gets linked to said PR.

The action generating the website runs each day at midnight. Do check the
original on Hydra, because Bioconductor packages are not listed, nor packages
for which somehow {packageRank} can't find a ranking. If the pull request
doesn't follow the naming convention "rPackages.packagename: blab bal" it likely
won't show up here.

```{r, echo = FALSE}
targets::tar_load(final_results)

reactable::reactable(final_results,
  columns = list(build = reactable::colDef(html = TRUE),
                 PR = reactable::colDef(html = TRUE)),
  defaultSorted = "rank",
  filterable = TRUE
)

```

Source code: https://github.com/b-rodrigues/nixpkgs-r-updates-fails

Rendered last: `r Sys.time()`
